Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-15 inc/extension/implementation/implementation.tex
typos (Jeff Berger++)

Additionally, a development version of the bin model presented in Section \ref{sec:bin_model} is available at \url{https://github.com/jberger/Physics-Photoemission}.
Once I am sufficiently confident in its implementation, and more importantly its voracity, I intend to release it to the CPAN as well, most likely under the name \verb!Physics::Photoemission!.
This module depends on the much larger Perl project PDL (\url{http://pdl.perl.org}), a matrix-oriented numerical library, making it slightly more difficult to install, however the speed and implementational simplicity benefit added by that dependency is marked.
Of particular interest to users of \verb!Physics::UEMColumn!, \verb!Physics::Photoemission! also includes a subclass of \verb!Physics::UEMColumn::Photoemission! which uses this binning model to generate the pulse's $z$ direction initial conditions.

>>>>

Additionally, a development version of the bin model presented in Section \ref{sec:bin_model} is available at \url{https://github.com/jberger/Physics-Photoemission}.
Once I am sufficiently confident in its implementation, and more importantly its veracity, I intend to release it to the CPAN as well, most likely under the name \verb!Physics::Photoemission!.
This module depends on the much larger Perl project PDL (\url{http://pdl.perl.org}), a matrix-oriented numerical library, making it slightly more difficult to install, however the speed and implementational simplicity benefit added by that dependency is marked.
Of particular interest to users of \verb!Physics::UEMColumn!, \verb!Physics::Photoemission! also includes a subclass of \verb!Physics::UEMColumn::Photoemission! which uses this binning model to generate the pulse's $z$ direction initial conditions.

### 2013-04-15 inc/model_results/lens_charge/lens_charge.tex
typos (Jeff Berger++)

In the transverse spatial dimension, space-charge effects that increase $ \sigma_{ \smallT } $ can be compensated for by using magnetic electron lenses~\cite{oudheusden_electron_2007,lagrange_nanosecond_2008}.
In an UEM, of course, the electron pulse will also need to be focused onto the specimen --- the focal spot size, post specimen image magnification, and CCD detector pix elation determining the spatial resolution in a TEM geometry~\cite{berger_dc_2009}.
The extent to which space-charge effects limit the focal fidelity is expected to be dependent upon both $N$ and the pulse shape (i.e., the pulse's space-time eccentricity), while still subject to Liouville's Theorem (see Section \ref{sec:liouville}).

>>>>

In the transverse spatial dimension, space-charge effects that increase $ \sigma_{ \smallT } $ can be compensated for by using magnetic electron lenses~\cite{oudheusden_electron_2007,lagrange_nanosecond_2008}.
In an UEM, of course, the electron pulse will also need to be focused onto the specimen --- the focal spot size, post specimen image magnification, and CCD detector pixelation determining the spatial resolution in a TEM geometry~\cite{berger_dc_2009}.
The extent to which space-charge effects limit the focal fidelity is expected to be dependent upon both $N$ and the pulse shape (i.e., the pulse's space-time eccentricity), while still subject to Liouville's Theorem (see Section \ref{sec:liouville}).
